---
title: "HIV Testing Analysis in PROSPECT Study"

subtitle: "Analysis of HIV testing outcomes in PROSPECT Study"

author: |
  | Peter MacPherson
  |
  | Liverpool School of Tropical Medicine, Liverpool, UK
  | Malawi-Liverpool-Wellcome Clinical Research Programme, Blantyre, Malawi
  |

date: | 
  | `r format(Sys.time(), "%B %d, %Y")`
  |
  | Table of Contents:
output: 
  html_document:
    theme: cosmo
    toc: true
---

<br>

## 1. Backgound

BACKGROUND TEXT HERE

<br>

## 2. Set-up

Load all required packages for analysis.

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)    #for data manipulation
library(janitor)      #for tables
library(pmthemes)     #for ggplot themes
library(knitr)        #for tables
library(rethinking)   #for statistical modelling
library(hiv.prospect) #for study data
library(arsenal)      #for table 1
library(brms)
library(sjPlot)

```

<br>

## 3. Import datasets

Import data required for the analysis.

```{r import}
data("entry", package = "hiv.prospect")
data("exit", package = "hiv.prospect")

```

<br>

## 4. Characteristics of attenders

In total, between 15th May 2018 and 7th September 2018 inclusive, there were a total of `r nrow(entry)` adult acute attendances at the study clinic (Bangwe Health Centre, Blantyre, Malawi).

What proportion of attendances were repeat attendances during the study period?

```{r}
entry %>%
  tabyl(reattendance) %>%
  kable(digits = 3, caption = "Proportion of attendances that were repeat")
```

What was the distribution of multiple visits by participants?

```{r}
entry %>%
  group_by(case_id) %>%
  mutate(sum_visits = sum(reattendance)+1) %>%
  tabyl(sum_visits) %>%
  kable(digits = 3, caption = "Distribution of visits")

```

What was the distribution of clinic visits by day?

```{r}

entry %>%
  group_by(received_on) %>%
  mutate(dailycount = n()) %>%
  summarise(dailymean = mean(dailycount)) %>%
  summarise(mean = mean(dailymean),
            min = min(dailymean),
            max = max(dailymean),
            median = median(dailymean))

```



Does the distribution of visits vary by characteristics (sex, cough, any TB symptoms?)

```{r}
entry %>%
  group_by(case_id) %>%
  mutate(sum_visits = sum(reattendance)+1) %>%
  tabyl(sum_visits, sex) %>%
  adorn_totals("col") %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable(digits = 3, caption = "Distribution of visits by sex")

```

```{r}
entry %>%
  group_by(case_id) %>%
  mutate(sum_visits = sum(reattendance)+1) %>%
  tabyl(sum_visits, cough) %>%
  adorn_totals("col") %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable(digits = 3, caption = "Distribution of visits by cough status")

```

```{r}
entry %>%
  group_by(case_id) %>%
  mutate(sum_visits = sum(reattendance)+1) %>%
  tabyl(sum_visits, any_symptoms) %>%
  adorn_totals("col") %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable(digits = 3, caption = "Distribution of visits by presence of any TB symptoms")

```


Now make a table of characteristics of attendance episodes

```{r}

table1 <- tableby(sex ~ 
                  age +
                  cough + 
                  weight_loss + 
                  fever +
                  night_sweats +
                  any_symptoms +
                  chronic_cough +
                  blantyre_res +
                  tb_rx +
                  tb_rx_6m,
                  data = entry,
                test = FALSE,
                numeric.stats = c("medianrange"))

kable(summary(table1), caption = "Table 1: Characteristics of attendance episodes by sex")



```

##5. Comparison of characteristics of those who did and did not undergo exit interview

First merge the datasets together - need to be careful to merge on participant id as well as date of attendance so as to match unique attendences among people who reattended.

```{r}

exit <- exit %>% mutate(interviewed = "Interviewed")

merged <- left_join(entry, exit, by = c("case_id", "received_on"))

merged <- merged %>%
  mutate(interviewed = case_when(is.na(interviewed) ~ "Not interviewed",
                                 TRUE ~ interviewed))

table2 <- tableby(interviewed ~ 
                  sex + 
                  age +
                  cough + 
                  weight_loss + 
                  fever +
                  night_sweats +
                  any_symptoms +
                  chronic_cough +
                  blantyre_res +
                  tb_rx +
                  tb_rx_6m,
                  data = merged,
                test = FALSE,
                numeric.stats = c("medianrange"),
                cat.stats = "countrowpct")

kable(summary(table2), caption = "Table 2: Comparison between participants who were and were not exit interviewed")

```



##6. Analysis of outcome


First how many were on ART? These will need to be filtered out as they are not eligibile for offer of HIV test

```{r}

merged %>% tabyl(art) %>% kable()

```


```{r}

outdata <- merged %>%
  filter(interviewed =="Interviewed") %>%
  filter(art == "No")

```

Now, of those remaining, how many are HIV-positive, but not on ART (these should be eligible for HIV testing)

```{r}

outdata %>% tabyl(hivstatus) %>% kable()

```

Now look at what proportion was offered HIV testing

```{r}

outdata %>% tabyl(askhivtest) %>% kable()

```

And what proportion actually did report HIV testing on same day?

```{r}

outdata %>% tabyl(testedhiv) %>% kable()

```

Compare characteristics between those offered and not offered HIV testing.

```{r}

table3 <- tableby(askhivtest ~ 
                  sex + 
                  age +
                  cough + 
                  weight_loss + 
                  fever +
                  night_sweats +
                  any_symptoms +
                  chronic_cough +
                  srh +
                  blantyre_res +
                  tb_rx +
                  tb_rx_6m +
                  prevtb +
                  everhivtest +
                  lasthivresult +
                  hivstatus,
                  data = merged,
                test = FALSE,
                numeric.stats = c("medianrange"),
                cat.stats = "countrowpct")

kable(summary(table3), caption = "Table 3: Comparison between participants who were and were not offered HIV testing during clinic attendance")


```

Compare characteristics between those reporting completing and not completing HIV testing.

```{r}

table4 <- tableby(testedhiv ~ 
                  sex + 
                  age +
                  cough + 
                  weight_loss + 
                  fever +
                  night_sweats +
                  any_symptoms +
                  chronic_cough +
                  srh +
                  blantyre_res +
                  tb_rx +
                  tb_rx_6m +
                  prevtb +
                  everhivtest +
                  lasthivresult +
                  hivstatus,
                  data = merged,
                test = FALSE,
                numeric.stats = c("medianrange"),
                cat.stats = "countrowpct")

kable(summary(table4), caption = "Table 4: Comparison between participants who reported completing and not completing HIV testing")


```


<br>

##7. Statistical modelling

Bayesian regression models
 
```{r}

outdata <- as.data.frame(outdata)

outdata <- outdata %>%
  mutate(sex2 = case_when(sex=="Male" ~ 1,
                          sex=="Female" ~ 2)) %>%
  mutate(prevtb2 = case_when(prevtb=="Yes" ~2,
                             prevtb=="No" ~ 1)) %>%
  mutate(everhivtest2 = case_when(everhivtest=="Yes" ~ 2,
                                  everhivtest=="No" ~ 1)) %>%
  mutate(any_symptoms2 = case_when(any_symptoms==TRUE ~ 1,
                                   any_symptoms==FALSE ~ 2)) %>%
  mutate(testedhiv2 = case_when(testedhiv=="Yes" ~1,
                                testedhiv=="No" ~ 0)) %>%
  mutate(cough2 = case_when(cough=="Yes" ~ 2,
                            cough=="No" ~ 1)) %>%
  mutate(chronic_cough2 = case_when(chronic_cough==TRUE ~ 1,
                                    chronic_cough==FALSE ~ 0))

outdata <- as.data.frame(outdata)

```


Model 1 - age and sex alone.

```{r}
mr1 <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5)),
  data=outdata, chains = 3)

precis(mr1)
plot(mr1)
plot(precis(mr1))

post_mr1_means <- as_tibble(as.list(coef(mr1))) %>% mutate_all(exp)
post_mr1_means <- post_mr1_means %>%
  mutate(rowname = "mean")

post_mr1 <- extract.samples(mr1, pars = c("a", "b_sex", "b_age"))

post_mr1_sum <- purrr::map(post_mr1, ~ PI(.x, prob = 0.89))
post_mr1_sum <- purrr::map(post_mr1_sum, ~ exp(.x))
post_mr1_sum <- data.frame(post_mr1_sum) %>% rownames_to_column()

post_mr1_sum <- bind_rows(post_mr1_sum, post_mr1_means) %>%
  mutate(model="mr1")


```

Men appear more likely to complete testing that women. And decrease in the probability of testing by age.

Model 2a - now add in cough of any duration.

```{r}

mr2a <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_cough*cough2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_cough ~ dnorm(0,2.5)
    ),
  data=outdata, chains = 3)

precis(mr2a)
plot(mr2a)
plot(precis(mr2a))

post_mr2a_means <- as_tibble(as.list(coef(mr2a))) %>% mutate_all(exp)
post_mr2a_means <- post_mr2a_means %>%
  mutate(rowname = "mean")

post_mr2a <- extract.samples(mr2a, pars = c("a", "b_sex", "b_age", "b_cough"))

post_mr2a_sum <- purrr::map(post_mr2a, ~ PI(.x, prob = 0.89))
post_mr2a_sum <- purrr::map(post_mr2a_sum, ~ exp(.x))
post_mr2a_sum <- data.frame(post_mr2a_sum) %>% rownames_to_column()

post_mr2a_sum <- bind_rows(post_mr2a_sum, post_mr2a_means) %>%
  mutate(model="mr2a")

```

As we would expect, individuals reporting cough of any duration had a greater posterior probability of completing HIV testing.

Model 2b - try adjusting for the effect of previous TB treatment

```{r}

mr2b <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_cough*cough2 +
      b_prevtb*prevtb2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_cough ~ dnorm(0,2.5),
    b_prevtb ~ dnorm(0,2.5)),
  data=outdata, chains = 3)

precis(mr2b)
plot(mr2b)
plot(precis(mr2b))

post_mr2b_means <- as_tibble(as.list(coef(mr2b))) %>% mutate_all(exp)
post_mr2b_means <- post_mr2b_means %>%
  mutate(rowname = "mean")

post_mr2b <- extract.samples(mr2b, pars = c("a", "b_sex", "b_age", "b_cough",
                                            "b_prevtb"))

post_mr2b_sum <- purrr::map(post_mr2b, ~ PI(.x, prob = 0.89))
post_mr2b_sum <- purrr::map(post_mr2b_sum, ~ exp(.x))
post_mr2b_sum <- data.frame(post_mr2b_sum) %>% rownames_to_column()

post_mr2b_sum <- bind_rows(post_mr2b_sum, post_mr2b_means) %>%
  mutate(model="mr2b")
```

Model 2c - try adjusting for the effect of ever having previously tested for HIV

```{r}

mr2c <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_cough*cough2 +
      b_prevtb*prevtb2 + b_everhivtest*everhivtest2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_cough ~ dnorm(0,2.5),
    b_prevtb ~ dnorm(0,2.5),
    b_everhivtest ~ dnorm(0,2.5)
    ),
  data=outdata, chains = 3)

precis(mr2c)
plot(mr2c)
plot(precis(mr2c))

post_mr2c_means <- as_tibble(as.list(coef(mr2c))) %>% mutate_all(exp)
post_mr2c_means <- post_mr2c_means %>%
  mutate(rowname = "mean")

post_mr2c <- extract.samples(mr2c, pars = c("a", "b_sex", "b_age", "b_cough",
                                            "b_prevtb", "b_everhivtest"))

post_mr2c_sum <- purrr::map(post_mr2c, ~ PI(.x, prob = 0.89))
post_mr2c_sum <- purrr::map(post_mr2c_sum, ~ exp(.x))
post_mr2c_sum <- data.frame(post_mr2c_sum) %>% rownames_to_column()

post_mr2c_sum <- bind_rows(post_mr2c_sum, post_mr2c_means) %>%
  mutate(model="mr2c")


```



Model 3 - what about chronic cough (>2 weeks - "classic" TB passive case finding symptom)

```{r}

mr3a <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_chronic_cough*chronic_cough2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_chronic_cough ~ dnorm(0,2.5)),
  data=outdata, chains = 3)

precis(mr3a)
plot(mr3a)
plot(precis(mr3a))

post_mr3a_means <- as_tibble(as.list(coef(mr3a))) %>% mutate_all(exp)
post_mr3a_means <- post_mr3a_means %>%
  mutate(rowname = "mean")

post_mr3a <- extract.samples(mr3a, pars = c("a", "b_sex", "b_age", "b_chronic_cough"))

post_mr3a_sum <- purrr::map(post_mr3a, ~ PI(.x, prob = 0.89))
post_mr3a_sum <- purrr::map(post_mr3a_sum, ~ exp(.x))
post_mr3a_sum <- data.frame(post_mr3a_sum) %>% rownames_to_column()

post_mr3a_sum <- bind_rows(post_mr3a_sum, post_mr3a_means) %>%
  mutate(model="mr3a")


```

Opposite pattern - individuals with chronic cough less likely to complete HIV testing. Might this be because they are taking TB treatment already (and so might have already been recently tested for HIV?)

```{r}

outdata %>%
  tabyl(chronic_cough2, prevtb) %>%
  adorn_totals("col") %>%
  adorn_totals("row") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns() %>%
  kable(digits = 3)

```

So looks like a strong relationship between previous tb and chronic cough. 

Model 3b - Try adding in previous TB as a term.

```{r}

mr3b <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_chronic_cough*chronic_cough2 +
      b_prevtb*prevtb2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_chronic_cough ~ dnorm(0,2.5),
    b_prevtb ~ dnorm(0,2.5)),
  data=outdata, chains = 3)

precis(mr3b)
plot(mr3b)
plot(precis(mr3b))

post_mr3b_means <- as_tibble(as.list(coef(mr3b))) %>% mutate_all(exp)
post_mr3b_means <- post_mr3b_means %>%
  mutate(rowname = "mean")

post_mr3b <- extract.samples(mr3b, pars = c("a", "b_sex", "b_age", "b_chronic_cough",
                                            "b_prevtb"))

post_mr3b_sum <- purrr::map(post_mr3b, ~ PI(.x, prob = 0.89))
post_mr3b_sum <- purrr::map(post_mr3b_sum, ~ exp(.x))
post_mr3b_sum <- data.frame(post_mr3b_sum) %>% rownames_to_column()

post_mr3b_sum <- bind_rows(post_mr3b_sum, post_mr3b_means) %>%
  mutate(model="mr3b")

```

Model 3c - add in ever previously tested for HIV

```{r}


mr3c <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_chronic_cough*chronic_cough2 +
      b_prevtb*prevtb2 + b_everhivtest*everhivtest2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_chronic_cough ~ dnorm(0,2.5),
    b_prevtb ~ dnorm(0,2.5),
    b_everhivtest ~ dnorm(0,2.5)
    ),
  data=outdata, chains = 3)

precis(mr3c)
plot(mr3c)
plot(precis(mr3c))

post_mr3c_means <- as_tibble(as.list(coef(mr3c))) %>% mutate_all(exp)
post_mr3c_means <- post_mr3c_means %>%
  mutate(rowname = "mean")

post_mr3c <- extract.samples(mr3c, pars = c("a", "b_sex", "b_age", "b_chronic_cough",
                                            "b_prevtb", "b_everhivtest"))

post_mr3c_sum <- purrr::map(post_mr3c, ~ PI(.x, prob = 0.89))
post_mr3c_sum <- purrr::map(post_mr3c_sum, ~ exp(.x))
post_mr3c_sum <- data.frame(post_mr3c_sum) %>% rownames_to_column()

post_mr3c_sum <- bind_rows(post_mr3c_sum, post_mr3c_means) %>%
  mutate(model="mr3c")


```



Model 4a - what about individuals with any symptoms of TB (cough, fever, weight loss, or night sweats)

```{r}

mr4a <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_anysymptoms*any_symptoms2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_anysymptoms ~ dnorm(0,2.5)),
  data=outdata, chains = 3)

precis(mr4a)
plot(mr4a)
plot(precis(mr4a))

post_mr4a_means <- as_tibble(as.list(coef(mr4a))) %>% mutate_all(exp)
post_mr4a_means <- post_mr4a_means %>%
  mutate(rowname = "mean")

post_mr4a <- extract.samples(mr4a, pars = c("a", "b_sex", "b_age", "b_anysymptoms"))

post_mr4a_sum <- purrr::map(post_mr4a, ~ PI(.x, prob = 0.89))
post_mr4a_sum <- purrr::map(post_mr4a_sum, ~ exp(.x))
post_mr4a_sum <- data.frame(post_mr4a_sum) %>% rownames_to_column()

post_mr4a_sum <- bind_rows(post_mr4a_sum, post_mr4a_means) %>%
  mutate(model="mr4a")

```

Model 4b - add in previous TB

```{r}

mr4b <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_anysymptoms*any_symptoms2 +
      b_prevtb*prevtb2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_anysymptoms ~ dnorm(0,2.5),
    b_prevtb ~ dnorm(0,2.5)
    ),
  data=outdata, chains = 3)

precis(mr4b)
plot(mr4b)
plot(precis(mr4b))

post_mr4b_means <- as_tibble(as.list(coef(mr4b))) %>% mutate_all(exp)
post_mr4b_means <- post_mr4b_means %>%
  mutate(rowname = "mean")

post_mr4b <- extract.samples(mr4b, pars = c("a", "b_sex", "b_age", "b_anysymptoms",
                                            "b_prevtb"))

post_mr4b_sum <- purrr::map(post_mr4b, ~ PI(.x, prob = 0.89))
post_mr4b_sum <- purrr::map(post_mr4b_sum, ~ exp(.x))
post_mr4b_sum <- data.frame(post_mr4b_sum) %>% rownames_to_column()

post_mr4b_sum <- bind_rows(post_mr4b_sum, post_mr4b_means) %>%
  mutate(model="mr4b")

```


Model 4c - add in ever previously HIV tested

```{r}

mr4c <- map2stan(
  alist(
    testedhiv2 ~ dbinom(1, p),
    logit(p) <- a + b_sex*sex2 + b_age*age + b_anysymptoms*any_symptoms2 +
      b_prevtb*prevtb2 + b_everhivtest*everhivtest2,
    a ~dnorm(0,100),
    b_sex ~ dnorm(0,2.5),
    b_age ~ dnorm(0,2.5),
    b_anysymptoms ~ dnorm(0,2.5),
    b_prevtb ~ dnorm(0,2.5),
    b_everhivtest ~ dnorm(0,2.5)
    ),
  data=outdata, chains = 3)

precis(mr4c)
plot(mr4c)
plot(precis(mr4c))

post_mr4c_means <- as_tibble(as.list(coef(mr4c))) %>% mutate_all(exp)
post_mr4c_means <- post_mr4c_means %>%
  mutate(rowname = "mean")

post_mr4c <- extract.samples(mr4c, pars = c("a", "b_sex", "b_age", "b_anysymptoms",
                                            "b_prevtb", "b_everhivtest"))

post_mr4c_sum <- purrr::map(post_mr4c, ~ PI(.x, prob = 0.89))
post_mr4c_sum <- purrr::map(post_mr4c_sum, ~ exp(.x))
post_mr4c_sum <- data.frame(post_mr4c_sum) %>% rownames_to_column()

post_mr4c_sum <- bind_rows(post_mr4c_sum, post_mr4c_means) %>%
  mutate(model="mr4c")

```

Compare the models by estimating their WAIC statistics and weights

```{r}
rethinking::compare(mr1, mr2a, mr2b, mr2c, mr3a, mr3b, mr3c, mr4a, mr4b, mr4c)

```


So models 2c, 3c and 4c have the lowest WAIC and the greatest weights. Essentially, none of the other models have any weight.

Construct an ensemble model of mr2c, mr3c, mr4c, combining results according to Aikaike weights

Figure 2: Now plot the posterior distributions

```{r}

#A table of summaries of posteior distributions

bind_rows(post_mr1_sum, 
          post_mr2a_sum, post_mr2b_sum, post_mr2c_sum,
          post_mr3a_sum, post_mr3b_sum, post_mr3c_sum,
          post_mr4a_sum, post_mr4b_sum, post_mr4c_sum)


gdata <- bind_rows(post_mr2c_sum, post_mr3c_sum, post_mr4c_sum) %>%
  select(model, everything()) %T>%
  print %>%
  gather(parameter, value, -model, -rowname) %>%
  mutate(parameter = case_when(parameter=="b_age" ~ "Age (years)",
                               parameter=="b_sex" ~ "Male sex",
                               parameter=="b_prevtb" ~ "Previous TB",
                               parameter=="b_everhivtest" ~ "Previous HIV test",
                               parameter=="b_cough" ~ "Cough",
                               parameter=="b_chronic_cough" ~ "Chronic cough",
                               parameter=="b_anysymptoms" ~ "Any TB symptoms",
                               parameter=="a" ~ "Intercept")) %>%
  mutate(parameter = factor(parameter)) %>%
  mutate(parameter = fct_relevel(parameter,
                                 "Intercept",
                                 "Any TB symptoms",
                                 "Chronic cough",
                                 "Cough",
                                 "Previous HIV test",
                                 "Previous TB",
                                 "Male sex",
                                 "Age (years)"
                                 ))

gdata_means <- gdata %>%
  filter(rowname=="mean")

gdata_ranges <- gdata %>% 
  filter(rowname !="mean") %>%
  spread(rowname, value) %>%
  select(everything(), l = `5%`, h = `94%`)

glabels <- c(
  mr2c = "Model 1: Cough",
  mr3c = "Model 2: Chronic Cough",
  mr4c = "Model 3: Any TB symptoms"
)

ggplot() +
  geom_point(data=gdata_means, aes(x=value, y=parameter, colour=model)) +
  geom_segment(data=gdata_ranges, aes(y=parameter, yend=parameter, x=l, xend=h, colour=model)) +
  geom_vline(data=gdata, aes(xintercept=1), alpha=0.3, linetype="dashed") +
  facet_wrap(~model,
             labeller = labeller(model=glabels)) +
  scale_color_rail(palette="penzance") +
  scale_x_continuous(limits = c(0.1,3.0), breaks = c(0.5,1.0,1.5,2.0,2.5,3.0)) +
  theme_bw() +
  ylab("") +
  xlab("Odds ratio (89% posterior interval)") +
  theme(legend.position="none")

ggsave(file="fig2.png", width = 8, height = 6, dpi=300, 
       path = here::here("figures"))
  

```

Posterior predictions for age and sex for each model

```{r}

outdata <- outdata %>%
  mutate(chronic_cough2 = factor(chronic_cough2)) %>%
  mutate(any_symptoms2 = factor(any_symptoms2))


prior <- c(prior_string("normal(0,2.5)", class="b"),
           prior_(~normal(0,100), class= ~Intercept))

graph2c <- brm(bf(testedhiv2 ~
          sex +
          age +
          cough +
          prevtb +
          everhivtest),
          data=outdata, 
          family='bernoulli',
          prior = prior,
          iter=1000, warmup=500,
          chains=3,
          seed=1234)


g2c <- plot_model(graph2c, type = "pred", terms = c("age", "sex"),
                 title = "Model 2c: Cough",
                 axis.title = c("Age (years)", "Probability of HIV testing (89% interval)"),
           legend.title = "Sex",
           ci.lvl = 0.89,
           colors = c("steelblue", "firebrick"),
           show.legend = FALSE)

g2c <- g2c + theme_bw()

graph3c <- brm(bf(testedhiv2 ~
          sex +
          age +
          chronic_cough2 +
          prevtb +
          everhivtest),
          data=outdata, 
          family='bernoulli',
          prior = prior,
          iter=1000, warmup=500,
          chains=3,
          seed=1234)


g3c <- plot_model(graph3c, type = "pred", terms = c("age", "sex"),
                 title = "Model 3c: Chronic cough",
                 axis.title = c("Age (years)", ""),
           legend.title = "Sex",
           ci.lvl = 0.89,
           colors = c("steelblue", "firebrick"),
           show.legend = FALSE)

g3c <- g3c + theme_bw()


graph4c <- brm(bf(testedhiv2 ~
          sex +
          age +
          any_symptoms2 +
          prevtb +
          everhivtest),
          data=outdata, 
          family='bernoulli',
          prior = prior,
          iter=1000, warmup=500,
          chains=3,
          seed=1234)


g4c <- plot_model(graph4c, type = "pred", terms = c("age", "sex"),
                 title = "Model 4c: Any TB symptom",
                 axis.title = c("Age (years)", ""),
           legend.title = "Sex",
           ci.lvl = 0.89,
           colors = c("steelblue", "firebrick"))

g4c <- g4c + theme_bw()

library(patchwork)
g2c + g3c + g4c + plot_layout(ncol = 3)

ggsave(file="fig3.png", width = 10, height = 6, dpi=300, 
       path = here::here("figures"))


```



## 8. Reproducibility

This reproduction of the analysis was run by: 

```{r sysinfo, echo=FALSE, message=FALSE, comment=NA, warning=FALSE}

sysinfo <- Sys.info()

sysinfo <- data.frame(keyName=names(sysinfo), value=sysinfo, row.names=NULL)

sysinfo %>% kable()
```

Analysis was run at **`r Sys.time()`**, and using the following Session Info:

```{r sessioninfo, echo=FALSE, results='markdown', message=FALSE, comment=NA, warning=FALSE}
sessionInfo()
```
